---
title: "SGN Air Quality 2017"
author: "markdroes@gmail.com"
date: "February 1, 2018"
output: pdf_document
---

*data was obtained through the US EPA (https://airnow.gov/index.cfm?action=airnow.global_summary#Vietnam$Ho_Chi_Minh_City)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Packages
options(repos=structure(c(cran="https://ftp.osuosl.org/pub/cran/")))  
packages <- c("TSA", "imputeTS") 
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}  
lapply(packages, require, character.only=TRUE)

#Set filename
file2016<-"c:/Users/Mark/Documents/CSV/HoChiMinhCity_PM2.5_2016_YTD.CSV"
file2017<-"c:/Users/Mark/Documents/CSV/HoChiMinhCity_PM2.5_2017_YTD.CSV"
file2018<-"c:/Users/Mark/Documents/CSV/HoChiMinhCity_PM2.5_2018_YTD.CSV"
```

```{r}
#Reading in the 2017 hourly data
data.2016<-read.csv(file2016, sep = ';')[,c(3,8,9,11)]
data.2017<-read.csv(file2017)[,c(3,9,10,11)]
data.2018<-read.csv(file2018)[,c(3,9,10,11)]
#the 2016 data set is missing 743 obs. from 12/2016
dec.2016<-matrix(rep(c("2016-01",-999,-999,-999),743),nrow = 743, ncol = 4, byrow = T,
                 dimnames = list(c() , c("Date..LT.","AQI","AQI.Category","Raw.Conc.")))
#Bind data together row wise
data<-rbind(data.2016,dec.2016,data.2017,data.2018)

#Data diagnostics on data$AQI
sum(data$AQI <0)
#1213 points with negative AQI (value actually -999), clearly errors.
#only 7% missing data, so we're doing well here
#Will impute values using 'imputeTS' pkg

#First step, set -999 to NuLL so the values are missing:
data$AQI[data$AQI == -999] <- NA
data$Raw.Conc.[data$Raw.Conc. == -999] <- NA

#Next, turn the data into a TS object to make it useable with 'imputeTS'
#tsdata<-ts(data[,c(2,4)], frequency = 8760, start = 998)
#Finally, the imputation
#imputed<-na.kalman(tsdata, model = "auto.arima")

#write.csv(imputed, file = "sgn_air_imputed.CSV")

```

First, let's a basic breakdown of the data.  How many hours (data points) occured in 2017 where the air quality was "unhealthy for sensitive groups" or higher?

```{r}
imputed<-read.csv("C:/Users/Mark/Documents/CSV/sgn_air_imputed.CSV")[,c(2,3)]
#This line counts the number of instances where AQI > 100
length(which(imputed[,1] > 100))
```

4059 hours over 2 years, which breaks down to $\approx 84.5$ days a year.

To see if there's any clear trends, let's next plot the AQI across the 2017 year.

```{r}
plot(imputed[,1], type = 'l')
```

Unsuprisingly, this plot does not show us all that much.  Next, I will perform a decomposition of this time-series data.

```{r}
imputed.ts<-ts(imputed,frequency = 8760, start = 998)
stl(imputed[,1], s.window = "periodic")
```
